\section{Deliverables}
\paragraph{}
The following deliverables result from the afore mentioned aim and objectives.

\paragraph{Interim Report} The Interim Report gives an overview of the project topic, its current status and the project schedule.
\paragraph{XMPP Client Library} The XMPP Client Library implements the necessary functionality to connect to and communicate with an XMPP server.
\paragraph{Worker Library} The Worker Library implements the necessary functions for clients to receive data packets and send back results.
\paragraph{Feeder Library} The Feeder Library implements the necessary functions to send data packets to clients and receive results.
\paragraph{Feeder Frontend} The Feeder Frontend enables the operator to view real-time statistics of the grid operation.
\paragraph{Worker Sample Implementation} This is a program implementing an algorithm for prime factorisation utilising the Worker Library for requesting working data.
\paragraph{Feeder Sample Implementation} This program serves the Sample Wor\-ker with data to work on.
\paragraph{API Documentation of the XMPP Client Library} The documentation for the XMPP Client Library API.
\paragraph{API Documentation of the Worker Library} The documentation for $3^{rd}$-party programmers to use the Worker Library.
\paragraph{API Documentation of the Feeder Library} The documentation to implement a feeder using the Feeder Library.
\paragraph{Web-based Statistics Analysis Tool} This is a web-based tool to view client and feeder statistics such as processed data packets.
\paragraph{User Manual for the Statistics Analysis Tool} The manual for the Sta\-tis\-tics Analysis Tool.
\paragraph{Final Report} The Final Report reports on the final status of the project.
